\section{Artifacts and Reproducibility}

\label{sec:artifacts}

\subsection{Source Code Release}

Source code, configs, and datasets are released. Each experiment is keyed by a Git commit and a Lockchain root. Independent recomputation must reproduce $\mathrm{hash}(A) = \mathrm{hash}(\mu(O))$ within $10^{-3}$ tolerance; otherwise the claim is falsified.

\textbf{Repositories}:
\begin{itemize}
    \item \textbf{KNHK}: \texttt{https://github.com/seanchatmangpt/knhk} (hot-path engine, workflow engine, 43/43 patterns)
    \item \textbf{unrdf}: \texttt{https://github.com/unrdf/unrdf} (knowledge hooks, \RDF{}/SHACL validation)
    \item \textbf{ggen}: \texttt{https://github.com/seanchatmangpt/ggen} (bounded ontology-to-code projection)
    \item \textbf{Lockchain}: Integrated into KNHK and unrdf (cryptographic receipts)
\end{itemize}

\subsection{Configuration Files}

Workflow definitions, guard sets, ontology schemas, and deployment configs are released.

\textbf{Configurations}:
\begin{itemize}
    \item \textbf{Workflow Definitions}: Turtle/YAWL format workflow specifications
    \item \textbf{Guard Sets}: Ingress guard definitions (legality, budgets, chronology, causality)
    \item \textbf{Ontology Schemas}: OWL/SHACL schema definitions
    \item \textbf{Deployment Configs}: Production deployment configurations
\end{itemize}

\subsection{Datasets}

Test data, benchmark inputs, and validation sets are released.

\textbf{Datasets}:
\begin{itemize}
    \item \textbf{Test Data}: Synthetic and real-world knowledge graph data
    \item \textbf{Benchmark Inputs}: Standardized benchmark inputs for reproducibility
    \item \textbf{Validation Sets}: Validation sets for determinism and receipt verification
\end{itemize}

\subsection{Runbooks}

Deployment procedures, verification steps, and troubleshooting guides are released.

\textbf{Runbooks}:
\begin{itemize}
    \item \textbf{Deployment Procedures}: Step-by-step deployment instructions
    \item \textbf{Verification Steps}: Receipt verification and reproducibility procedures
    \item \textbf{Troubleshooting Guides}: Common issues and solutions
\end{itemize}

\subsection{Reproducibility Requirements}

Independent recomputation must reproduce $\mathrm{hash}(A) = \mathrm{hash}(\mu(O))$ within $10^{-3}$ tolerance. Divergence beyond $10^{-3}$ invalidates the run.

\textbf{Verification Process}:
\begin{enumerate}
    \item \textbf{Clone}: Clone repository at specified commit
    \item \textbf{Configure}: Load configuration from dataset
    \item \textbf{Execute}: Run experiment with same inputs
    \item \textbf{Verify}: Compare receipt hashes within tolerance
    \item \textbf{Validate}: Receipt delta $< 10^{-3}$ confirms reproducibility
\end{enumerate}

\subsection{Falsifiability}

Every experiment can be independently verified by recomputing the hash chain of operations. Divergence beyond $10^{-3}$ invalidates the run.

\textbf{Falsification Criteria}:
\begin{itemize}
    \item \textbf{Receipt Delta}: $> 10^{-3}$ tolerance
    \item \textbf{Hash Mismatch}: $\mathrm{hash}(A) \neq \mathrm{hash}(\mu(O))$
    \item \textbf{Determinism Violation}: $O_1 = O_2$ but $\mu(O_1) \neq \mu(O_2)$
    \item \textbf{Boundedness Violation}: Unbounded loop or non-terminating regeneration
\end{itemize}

\subsection{Authorship}

The law and system are introduced by \textbf{Sean Chatman}. Cite as: Chatman (2025), \textit{The Chatman Equation and the Industrial Revolution of Knowledge}.

\textbf{Attribution}:
\begin{itemize}
    \item \textbf{The Chatman Equation}: $A = \mu(O)$ introduced by Sean Chatman
    \item \textbf{Knowledge Hooks}: Unit of knowledge work introduced by Sean Chatman
    \item \textbf{Reflex Enterprise}: Complete stack implementation by Sean Chatman
    \item \textbf{43/43 Pattern Coverage}: Complete enterprise embodiment by Sean Chatman
\end{itemize}

\subsection{License}

All source code, configs, datasets, and runbooks are released under MIT License. See individual repositories for license details.

\subsection{Contact}

For questions, issues, or contributions, contact:
\begin{itemize}
    \item \textbf{Email}: \texttt{sean@chatman.ai}
    \item \textbf{GitHub}: \texttt{https://github.com/seanchatmangpt}
    \item \textbf{Issues}: See individual repositories for issue tracking
\end{itemize}

